---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


[![Travis-CI Build Status](https://travis-ci.org/fmichonneau/foghorn.svg?branch=master)](https://travis-ci.org/fmichonneau/foghorn)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/fmichonneau/foghorn?branch=master&svg=true)](https://ci.appveyor.com/project/fmichonneau/foghorn)
[![Coverage Status](https://img.shields.io/codecov/c/github/fmichonneau/foghorn/master.svg)](https://codecov.io/github/fmichonneau/foghorn?branch=master)
![Work in Progress](https://img.shields.io/badge/status-work in progress-yellow.svg)
[![](http://www.r-pkg.org/badges/version/foghorn)](http://www.r-pkg.org/pkg/foghorn)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# foghorn

> **foghorn** *noun* <br>
>     1. Device used to facilitate navigation in foggy conditions by warning of
>        potential hazards ahead.

`foghorn` makes accessible to the R terminal the results of the CRAN check
results for the packages maintained by individuals, or for other package of
interests. It provides a graphical summary of the results designed to added to
your `.Rprofile` (to check regularly on the status of the published packages),
or as a tibble.

As new features are introduced in development versions of R, or new policies are
put in place, packages that are not updated frequently may start generating
warnings or errors when built by CRAN. `foghorn` brings this information to your
terminal automatically so you don't have to check the CRAN check results page
regularly.

The package uses [whoami](https://cran.r-project.org/package=whoami) to guess
your email address, but it can be specified manually.

## Installation

You can install foghorn from github with:

```{r gh-installation, eval = FALSE}
# install.packages("ghit")
ghit::install_github("fmichonneau/foghorn")
```

## Example

```{r example}
## load the package
library(foghorn)

## Graphical interface
summary_cran_checks(email = "francois.michonneau@gmail.com")

## Summary as a data frame
cran_check_results(email = "francois.michonneau@gmail.com")

## You can also have information just for some packages
summary_cran_checks(email = NULL,  package = c("mregions", "ridigbio"))
cran_check_results(email = NULL,  package = c("mregions", "ridigbio"))

## Or both
summary_cran_checks(email = "francois.michonneau@gmail.com",  package = c("mregions", "ridigbio"))
cran_check_results(email = "francois.michonneau@gmail.com",  package = c("mregions", "ridigbio"))

## You can also get the results details of the check results for packages:
summary_cran_results("rotl")
```
