---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->


[![Travis-CI Build Status](https://travis-ci.org/fmichonneau/foghorn.svg?branch=master)](https://travis-ci.org/fmichonneau/foghorn)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# foghorn

> **foghorn** *noun* Device used to facilitate navigation in foggy conditions.

`foghorn` makes accessible to the R terminal the results of the CRAN check
results for the packages maintained by individuals, or for other package of
interests. It provides a graphical summary of the results designed to added to
your .Rprofile (to check regularly on the status of the published packages), or
as a tibble.

The package uses [whoami](https://cran.r-project.org/package=whoami) to guess
your email address, but addresses can be added manually.

## Installation

You can install foghorn from github with:

```{r gh-installation, eval = FALSE}
# install.packages("ghit")
ghit::install_github("fmichonneau/foghorn")
```

## Example

```{r example}
## load the package
library(foghorn)

## Graphical interface
summary_cran_checks(email = "francois.michonneau@gmail.com")

## Summary as a tibble
cran_check_results(email = "francois.michonneau@gmail.com")

## You can also have information just for some packages
summary_cran_checks(email = NULL,  package = c("mregions", "ridigbio"))
cran_check_results(email = NULL,  package = c("mregions", "ridigbio"))

## Or both
summary_cran_checks(email = "francois.michonneau@gmail.com",  package = c("mregions", "ridigbio"))
cran_check_results(email = "francois.michonneau@gmail.com",  package = c("mregions", "ridigbio"))
```
