---
title: "Get started"
author: "Francois Michonneau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r example}
## load the package
library(foghorn)
```

`foghorn` provides the results of the package CRAN checks. As a maintainer, you can easily get the results of the checks for your packages by using the email address included in the `DESCRIPTION` file of your packages. 

`summary_cran_results()` provides you with a graphical summary of the results of the CRAN checks. The number in parenthesis after the name of the package indicates the number of platforms used by CRAN that produced this result.

```{r graphical-interface}
## Graphical interface
summary_cran_results(email = "francois.michonneau@gmail.com")
```

`summary_cran_results()` is actually an alias of `summary(cran_results())`, meaning that you can call `cran_results()` directly if you want to easily access the underlying data for the results of the CRAN checks. These results are stored in a tibble.

```{r tibble}
## Results as a tibble
cran_results(email = "francois.michonneau@gmail.com")
```

In addition of your own packages, you can also check the results for any other
packages that might be of interest to you:

```{r package-name}
## either by themselves
summary_cran_results(pkg = c("ggplot2", "dplyr"))
cran_results(pkg = c("ggplot2", "dplyr"))

## or by combining them with email addresses
summary_cran_results(email = "francois.michonneau@gmail.com",
                     pkg = c("mregions", "ridigbio"))
cran_results(email = "francois.michonneau@gmail.com",
                   pkg = c("mregions", "ridigbio"))
```

You can inspect the logs for the check results using
`summary_cran_details(pkg)` (or `summary(cran_details(pkg))`), while `visit_cran_check(pkg)` takes you directly to the CRAN webpage.


```{r cran-details}
tidyr_details <- cran_details(pkg = "tidyr")
tidyr_details
summary(tidyr_details)
```

## Where does it get the data?

The data from the check results used by this package are either scrapped from
the CRAN web pages (default), or are from the CRAN database (that CRAN uses to
build the webpages). The first option is faster if you want to regularly check a
few packages. However, if you are doing statistics on a large number of
packages, using the CRAN database is recommended (it's about 20Mb of data). To
use the CRAN database, add `src = "crandb"` in your function calls:

```{r show-cran-db, eval=FALSE}
cran_results(pkg = "nlme", src = "crandb")
```

Check out the "Details" section in the help files for more information.


## Feedback? Suggestions?

Feel free to submit feedback and suggestions
by [opening an issue](https://github.com/fmichonneau/foghorn/issues/new) on
GitHub.
