---
title: "Quick start"
author: "Francois Michonneau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r example}
## load the package
library(foghorn)
```

`foghorn` provides a graphical summary for CRAN check results for the packages
maintained by individuals (the number is parentheses indicates the number of R
flavors used by CRAN that generate notes, warnings, errors):

```{r graphical-interface}
## Graphical interface
summary_cran_results(email = "francois.michonneau@gmail.com")
```

The information can also be summarized as a table:

```{r tibble}
## Summary as a tibble
cran_results(email = "francois.michonneau@gmail.com")
```

In addition of your own packages, you can also check the results for other
packages that might be of interest to you:

```{r package-name}
## either by themselves
summary_cran_results(pkg = c("ggplot2", "dplyr"))
cran_results(pkg = c("ggplot2", "dplyr"))

## or by combining them with email addresses
summary_cran_results(email = "francois.michonneau@gmail.com",
                     pkg = c("mregions", "ridigbio"))
cran_results(email = "francois.michonneau@gmail.com",
                   pkg = c("mregions", "ridigbio"))
```

You can also inspect the logs for the check results using
`summary(cran_details(pkg))`, while `visit_cran_check(pkg)` takes you to the CRAN
webpage.

```{r cran-details}
tidyr_details <- cran_details(pkg = "tidyr")
tidyr_details
summary(tidyr_details)
```

## Where does it get the data?

The data from the CRAN check results used by this package are either scrapped
from the CRAN web pages (default), or are from the CRAN database. The first
option is faster if you want to check regularly a few packages. However, if you
are doing statistics on a large number of packages, using the CRAN database is
recommended. To use the CRAN database, add `src = "crandb"` in your function
calls:

```{r show-cran-db}
cran_results(pkg = "nlme", src = "crandb")
```

Check out the "Details" section in the help files for more information.


## Feedback? Suggestions?

Feel free to submit feedback and suggestions
by [opening an issue](https://github.com/fmichonneau/foghorn/issues/new) on
GitHub.
