---
title: "Quick start"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r example}
## load the package
library(foghorn)
```

`foghorn` provides a graphical summary for CRAN check results for the packages
maintained by individuals (the number is parentheses indicates the number of R
flavors used by CRAN that generate notes, warnings, errors):

```{r graphical-interface}
## Graphical interface
summary_cran_results(email = "francois.michonneau@gmail.com")
```

The information can also be summarized as a table:

```{r tibble}
## Summary as a tibble
check_cran_results(email = "francois.michonneau@gmail.com")
```

In addition of your own packages, you can also check the results for other
packages that might be of interest to you:

```{r package-name}
## either by themselves
summary_cran_results(pkg = c("ggplot2", "dplyr"))
check_cran_results(pkg = c("ggplot2", "dplyr"))

## or by combining them with email addresses
summary_cran_results(email = "francois.michonneau@gmail.com",
                     pkg = c("mregions", "ridigbio"))
check_cran_results(email = "francois.michonneau@gmail.com",
                   pkg = c("mregions", "ridigbio"))
```

You can also inspect the logs for the check results using
`show_cran_results(pkg)`, while `visit_cran_check(pkg)` takes you to the CRAN
webpage.

```{r show-cran-results}
show_cran_results(pkg = "tidyr")
```

## Feedback? Suggestions?

Feel free to submit feedback and suggestions
by [opening an issue](https://github.com/fmichonneau/foghorn/issues/new) on
GitHub.
